---
title: "Try different models/split_methods on the hillstorm dataset"
output: html_document
---

```{r, message=FALSE, include=FALSE}
library(uplift)
library(dplyr)
library(caret)
```

##Preparing the data
```{r}
hillstrom <- read.csv("datasets/Hillstrom.csv")
str(hillstrom)

##change some of the ints to factors
hillstrom$mens <- as.factor(hillstrom$mens)
hillstrom$womens <- as.factor(hillstrom$womens)
hillstrom$newbie <- as.factor(hillstrom$newbie)
hillstrom$visit <- as.factor(hillstrom$visit)

str(hillstrom)

##conversion is a stronger outcome than visit
target <- 'conversion'

##treatment variable must be in binary format and take values 0/1
hillstrom <- hillstrom %>% mutate(treatment = ifelse(segment == 'No E-Mail', 0, 1))
hillstrom$segment <- NULL

#split
inTrain <- createDataPartition(hillstrom$conversion, p = 0.7, list = F)
hillstrom_train <- hillstrom[inTrain, ]
hillstrom_test <- hillstrom[-inTrain, ]

#create formula
predictors <- setdiff(names(hillstrom), c(target, 'treatment'))
formula <- reformulate(termlabels = c(predictors, 'trt(treatment)'), response = target)
```

##Explore data for uplift modeling
```{r}
explore(formula, hillstrom_train)
```

####For plotting uplift curves
```{r}
plot_uplift <- function(model_fit, test_data) {
  pred_RF <- predict(model_fit, test_data)
  uplift_RF <- pred_RF[, 1] - pred_RF[, 2]
  with_predictions = data.frame(test_data, uplift_RF)
  #modelProfile(reformulate(predictors, response = 'uplift_RF'), data = with_predictions, group_label = "D")
  
  perf <- performance(pred_RF[, 1], pred_RF[, 2], with_predictions$conversion, with_predictions$treatment)
  plot(perf[, 8] ~ perf[, 1], type ="l", xlab = "Decile", ylab = "uplift")
}
```

#RF

###Splitting method: Chisq
```{r}
fit_RF_Chisq <- upliftRF(formula, hillstrom_train, split_method="Chisq")
summary(fit_RF_Chisq)
```

```{r}
plot_uplift(fit_RF_Chisq, hillstrom_test)
```

###Splitting method: ED (Eucledian Dist)
```{r}
fit_RF_ED <- upliftRF(formula, hillstrom_train, split_method="ED")
summary(fit_RF_ED)
```

```{r}
plot_uplift(fit_RF_ED, hillstrom_test)
```

###Splitting method: KL (Kullback-Leibler divergence)
```{r}
fit_RF_KL <- upliftRF(formula, hillstrom_train, split_method="KL")
summary(fit_RF_KL)
```

```{r}
plot_uplift(fit_RF_KL, hillstrom_test)
```


###Splitting method: Int (Interaction method)
```{r}
fit_RF_Int <- upliftRF(formula, hillstrom_train, split_method="Int")
summary(fit_RF_Int)
```

```{r}
plot_uplift(fit_RF_Int, hillstrom_test)
```


#ccif

###Splitting method: Chisq
```{r}
fit_ccif_Chisq <- ccif(formula, hillstrom_train, split_method="Chisq")
summary(fit_ccif_Chisq)
```

```{r}
plot_uplift(fit_ccif_Chisq, hillstrom_test)
```

###Splitting method: ED (Eucledian Dist)
```{r}
fit_ccif_ED <- ccif(formula, hillstrom_train, split_method="ED")
summary(fit_ccif_ED)
```

```{r}
plot_uplift(fit_ccif_ED, hillstrom_test)
```

###Splitting method: KL (Kullback-Leibler divergence)
```{r}
fit_ccif_KL <- ccif(formula, hillstrom_train, split_method="KL")
summary(fit_ccif_KL)
```

```{r}
plot_uplift(fit_ccif_KL, hillstrom_test)
```


###Splitting method: Int (Interaction method)
```{r}
fit_ccif_Int <- ccif(formula, hillstrom_train, split_method="Int")
summary(fit_ccif_Int)
```

```{r}
plot_uplift(fit_ccif_Int, hillstrom_test)
```


#knn [Extremely slow, eats up memory]

```{r, eval=FALSE}
fit_knn <- upliftKNN(hillstrom_train, hillstrom_test, hillstrom_train$conversion, hillstrom_train$treatment, k = 3)
summary(fit_knn)
```
